Random Forests", OAs

### 2024-07-07 src/oa_RF_corrected.Rmd
all corrected but regions

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#   2     variance    2.307827  0.2770946  0.7497850
#   2     extratrees  2.329867  0.2306295  0.7719781
#   5     variance    2.432873  0.2744482  0.7596487
#   5     extratrees  2.409776  0.2344573  0.7960409
#   8     variance    2.486179  0.2616929  0.7571522
#   8     extratrees  2.452737  0.2318285  0.8086679
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance and min.node.size = 5.

>>>>

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#   2     variance    1.221299  0.4082199  0.5829598
#   2     extratrees  1.308769  0.3297824  0.6136490
#   5     variance    1.203082  0.4241359  0.5703508
#   5     extratrees  1.280883  0.3513153  0.6124031
#   8     variance    1.214268  0.4155308  0.5674246
#   8     extratrees  1.284107  0.3502621  0.6180390
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance and
#  min.node.size = 5.

### 2024-07-07 src/oa_RF_corrected_10.Rmd
all corrected but regions

# df9610 %>% filter(V1.domain == 1) %>% 
#   left_join(lookup, by = "pc", suffix =c("","")) %>% 
#   filter(ladcd == "E08000006" & year == 2006) %>% 
#   group_by(pc) %>% 
#   summarise(n = n()) %>% 
#   arrange(desc(n))
# 
# df9610 %>% filter(pc == "M28 2SL" & year == 2006 & V1.domain == 1)

problem.pcs <- df9610 %>% filter(year > 1999 & year < 2011) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  # complete(pc, year) %>% 
  # replace(is.na(n), 0) %>% 
  arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010) %>% 
  slice_head(n=10) %>% 
  dplyr::select(pc)

# [1] "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"  "EC1V 4PY" "DE21 7BF" "E14 9SR"  "GL16 7YA" "WC1N 3XX"
# [10] "CB2 1AB" 
```

## Correct 1996-2010

@@

```{r}
df9610 <- df9610 %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df9610 <- pdata.frame(df9610)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df9610), newdata = df9610), 2)

df9610$n[is.na(df9610$n)] <- predictions[is.na(df9610$n)]
df9610 %>% filter(pc == "M28 2SL") %>% distinct(year)
```

## Load remaining data

```{r}
df9610 <- as_tibble(df9610) %>% 
  mutate(year = as.double(as.character(year))) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>%
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%            
  ungroup()

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    V1.domain < m,               # for multiple pc
    #V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%             # for n == 1  
  #summarise(n = sum(V1.domain)) %>% # for multiple pc  
  ungroup()

df <- bind_rows(df9610, df1112) %>% 
  filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

# tests for Scotland
# df %>% filter(substr(oa11cd, 1,1) =="S",
#               year==2010) %>% summarise(mean(n, na.rm = T))
# 
# df %>% filter(oa11cd=="S00090182")
# 
# test@data %>% filter(substr(id, 1,1) =="S",
#                      n!=0)
# 
# df %>% filter(substr(oa11cd, 1,1) =="W",
#               year==2003)
```

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    5.341123  0.3211637  1.294570
#   2     extratrees  5.114541  0.2727356  1.288928
#   5     variance    6.248341  0.3136499  1.380152
#   5     extratrees  5.584957  0.2834177  1.397949
#   8     variance    6.801851  0.2977672  1.395883
#   8     extratrees  5.957788  0.2811840  1.444036
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule
#  = extratrees and min.node.size = 5.

>>>>

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    V1.domain < m)               # for multiple pc
    #V1.domain == n)             # for n == 1

df.long <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = sum(V1.domain)) %>%
  ungroup() %>% 
  #arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_1996, n_1999, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010, n_2011, n_2012) %>%
  arrange(desc(n_2004), desc(n_2005)) %>% 
  slice_head(n=1000) %>% 
  pivot_longer(!pc, names_to = "year", values_to = "n") %>% 
  mutate(year = as.integer(sub("n_", "", year, fixed = TRUE))) %>% 
  replace(is.na(.), 0) %>% 
  mutate(outlier = ifelse(n > 1000 & (year==2004 | year == 2005), pc, ""))

# From n = 1 as these are the 'true' outliers
problem.pcs <- c("SE24 9HP", "CV8 2ED", "GL16 7YA", "CW1 6GL", "M28 2SL", "DE21 7BF")
```

## Corrected

@@

```{r}
df.corrected <- bind_rows(df9610, df1112) %>% 
  filter(year > 1995 & year < 2013) %>% 
  group_by(pc, year) %>% 
  summarise(n = sum(V1.domain)) %>% 
  ungroup() %>% 
  # The next line is different than the same for  n = 1: problem.pcs$pc
  mutate(n = ifelse(pc %in% as.character(problem.pcs) & year > 2003 & year <2007, NA, n))

df.corrected <- pdata.frame(df.corrected)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df.corrected), newdata = df.corrected), 2)

df.corrected$n[is.na(df.corrected$n)] <- predictions[is.na(df.corrected$n)]
```

## OA df

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = sum(n)) %>% # for multiple pc  
  ungroup() %>% 
  complete(oa11cd, year) %>% 
  filter(!is.na(oa11cd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#   2     variance    1.221299  0.4082199  0.5829598
#   2     extratrees  1.308769  0.3297824  0.6136490
#   5     variance    1.203082  0.4241359  0.5703508
#   5     extratrees  1.280883  0.3513153  0.6124031
#   8     variance    1.214268  0.4155308  0.5674246
#   8     extratrees  1.284107  0.3502621  0.6180390
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance
#  and min.node.size = 5.
